Check consistency

### 2023-08-03 FoodWebsCheck.Rmd
Add manuscript en markdown

#
dtot <- read_csv("Data/WeddellSea_links.csv")

# Check valid names 
#
#
require(taxize)
dfn <- unique(dtot$consumer)
con_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
# Species not found
anti_join(data.frame(user_supplied_name=dfn),con_names)
# 1 Cadulus dalli antarcticum

dfn <- unique(dtot$resource)
res_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
anti_join(data.frame(user_supplied_name=dfn),res_names)
# 1             Phytodetritus
# 2                  Sediment
# 3         Silicioflagellata
# 4 Cadulus dalli antarcticum

@@

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links_2.csv")
```

>>>>

#
dtot <- read_csv("Data/WeddellSea_links_original.csv")

# Check valid names 
#
# Predators
require(taxize)
dfn <- unique(dtot$consumer)
con_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
# Species not found
anti_join(data.frame(user_supplied_name=dfn),con_names)
# 1 Cadulus dalli antarcticum

# CLasificación completa
clasall <- classification(dfn, db = 'itis') #

# Preys
#
dfn <- unique(dtot$resource)
res_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
anti_join(data.frame(user_supplied_name=dfn),res_names)
# 1             Phytodetritus
# 2                  Sediment
# 3         Silicioflagellata
# 4 Cadulus dalli antarcticum

@@

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
```
